### 2018-04-03 Sections/encrypted_cloud_quantum_computing.tex
Bit of indexing
Added command for commenting.
Added bits to secure delegated qc section

The difference between the two protocols lies in the treatment of algorithms. In homomorphic encryption, Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which he would also like to keep to himself). In blind computing, Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret. Both of these protocols seem like very challenging goals, yet significant developments have been made on both fronts.

Classical homomorphic encryption has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}. \comment{What is the overhead in classical resources? What about classical blind computation -- impossible? Brief outline of how classical approach works.}

@@

\subsubsection{Blind computation} \index{Blind computation} \index{Blind quantum computation}

>>>>

The difference between the two protocols lies in the treatment of algorithms. In homomorphic encryption, Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which \sihui{in some cases} he would also like to keep to himself). \sihui{When any boolean circuit is allowed, the protocol is said to be a {\it fully} homomorphic encryption protocol (FHE). Otherwise, it is a somewhat-homomorphic encryption protocol.} In blind computing, Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret. Both of these protocols seem like very challenging goals, yet significant developments have been made on both fronts.

\sihui{Although homomorphic encryption protocols have been around for a few decades [cite], classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}. \sihui{In Gentry's seminal paper, he showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates.}

 \comment{What is the overhead in classical resources? What about classical blind computation -- impossible? Brief outline of how classical approach works.}

\sihui{[Comment: Classical blind computation is impossible.  ]}

@@

\subsubsection{Blind computation} \index{Blind quantum computation}
